---
title: "High level overview"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

caff <- read_csv("data/caffeineData.csv")
colnames(caff)[2] <- "score"
```

# Example of two group high level

## Experimental setup

A researcher wants to test whether caffeine consumption can help you perform better on exams. Two groups of n=`r length(caff$score)/2` were given a general knowledge exam. The morning of the exam, one group consumed caffeine and the other consumed a placebo. 

## Data summary 1: histograms

```{r, echo=FALSE}
ggplot(caff, aes(x=score, fill=group)) + geom_histogram(binwidth=1,alpha=.5)
```

## Data summary 2: Boxplots

```{r, echo=FALSE}
ggplot(caff, aes(x=group,y=score))+geom_boxplot()
```

## Inferential summary: Confidence interval plot

```{r, echo=FALSE}
caff %>% group_by(group) %>% summarize(N = n(), est = mean(score), ci=1.96*sd(score)/sqrt(N)) %>% ggplot(aes(x=group,y=est)) + geom_point() + geom_errorbar(aes(ymin=est-ci,ymax=est+ci))
```



# Example of X vs Y high level


