---
title: "Your 2-Group Project Title Here"
author: "Your Name Here"
output: html_notebook
---

> This is a template for you to use to make your short report of your analysis and findings. > When you see text like this, you can delete  it after you've read it.
> Before you move on, make sure you change the title and author above!

## Introduction
 
> Here, briefly describe what your project was about, and what your prediction was.
> This needn't be more than a single paragraph. 

> Load the tidyverse - always our first step!

```{r}
# load the tidyverse!
```

---

> In the code cell below, make a plot of the data distributions for the two groups 
  as either histograms or kde plots.
  > Briefly introduce the plot here.

```{r}
# plot of the data distributions

```

> Briefly interpret the plot here.

---

> Make a boxplot of your two groups below.
> Briefly introduce the plot first.

```{r}
# boxplot of the data

```

> Interpret the plot here

---

> Below, plot the means with 95% CIs.
> Briefly introduce the plot.

```{r}
# plot of the means with 95% confidence intervals

```

> Interpret the plot here - how should we interpret the separation of the means
> in terms of the confidence intervals?

---

> Compute a p-value assuming no true difference between the groups

```{r}
 # compute a p-value
```

> Interpret the p-value

---

> Finally, briefly summarize your findings.


